Adaptive Shrinkage and False Discovery Rates by Laplace Approximation

### 2013-11-01 Rcode/readme.rmd
added work on talk for NS lab meeting

>>>>

Try resampling the z scores from the alternative:
```{r}
  require(locfdr)
  hh.locfdr = locfdr(hh.zscore,nulltype=0)
  weights = 1-hh.locfdr$fdr
  altz = hh.zscore[runif(length(weights))<weights]
  hist(altz)
```

Directly modelling the z scores, without taking account of their errors,
leads to distributions under the
alternative that are simply implausible.
```{r}
  require("mixfdr")
  source("~/Documents/git/ash/Rcode/mix.R")
  altz.mixfdr = mixFdr(altz,noiseSD=1,J=100)
  g= normalmix(altz.mixfdr$pi,altz.mixfdr$mu,altz.mixfdr$sigma)
  x= seq(-8,8,length=100)
  par(mfcol=c(1,1))
  hist(altz,breaks = x,prob=TRUE)
  lines(x,dens(g,x),col=2)
```

Directly modelling the p values is maybe even worse?
Here we fit a monotonic decreasing function to the p values.
Then we subtract the uniform distribution (the null) away from this, to
give the alternative. 
```{r}
  hist(hh.pval,probability=TRUE,xlab="p value",main="Distribution of p values for Hedenfalk et al data",nclass=40,col=5)
  require(fdrtool)
  hh.fdrtool = fdrtool(hh.pval,statistic="pvalue")
  weights2 = 1-hh.fdrtool$lfdr
  altz2 = hh.zscore[runif(length(weights2))<weights2]
  hist(altz2,nclass=100)
  hist(altz,nclass=100)
  plot(hh.zscore,hh.locfdr$fdr)
  points(hh.zscore,hh.fdrtool$lfdr,col=2)
```

### 2013-11-01 talks/ilike-slides-plus.Rmd
added work on talk for NS lab meeting

>>>>

```{r}
library("DSS")
names(g)=colnames(cc)
designs=c(0,0,1,1)
names(designs)=colnames(cc)
seqData=newSeqCountSet(as.matrix(cc), designs)
seqData=estNormFactors(seqData)
seqData=estDispersion(seqData)
result=waldTest(seqData)
#note I edited waldTest to output std
z.dss=result$difExpr/result$std
z.dss[result$geneIndex]=result$difExpr/result$std
```
